% ************************** Thesis Abstract *****************************
% Use `abstract' as an option in the document class to print only the titlepage and the abstract.
\begin{abstract}
	% Context
	This thesis focuses on the application of Constraint Satisfaction and Optimization
	techniques in two Artificial Intelligence (AI) domains: automated design of elevator
	systems and verification of Neural Networks (NNs). The three main areas of interest
	for my work are $(i)$ the languages for defining the constraints for the systems, 
	$(ii)$ the algorithms and encodings that enable solving the problems considered and
	$(iii)$ the tools that implement such algorithms. 
	
	% Motivation
	Given the expressivity of the domain description languages and the availability of
	effective tools, several problems in diverse application fields have been solved 
	successfully using constraint satisfaction techniques. The two case studies herewith
	presented are no exception, even if they entail different challenges in the adoption
	of such techniques. Automated design of elevator systems not only requires encoding
	of feasibility (hard) constraints, but should also take into account design preferences, 
	which can be expressed in terms of cost functions whose optimal or near-optimal value
	characterizes ``good'' design choices versus ``poor'' ones.  Verification of NNs (and
	other machine-learned implements) requires solving large-scale constraint problems
	which may become the main bottlenecks in the overall verification procedure. 
	
	% Contribution
	This thesis proposes some ideas for tackling such challenges, including encoding 
	techniques for automated design problems and new algorithms for handling the optimization
	problems arising from verification of NNs. The proposed algorithms and techniques are
	evaluated experimentally by developing tools that are made available to the research
	community for further evaluation and improvement.
\end{abstract}
