% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      

    To all who helped the University of Genoa complete my master's thesis, I would like to take this opportunity to express my sincere gratitude.
    First and foremost, I want to express my gratitude to Prof. Armando Tacchella for his invaluable advice, steadfast support, and ongoing encouragement throughout this research process. He played a key role in the development of this thesis and my academic development with his knowledge, commitment, and patience. 
    Additionally, I would like to express my sincere gratitude to Stefano Demarchi, who served as my thesis advisor. His advice and expertise were very helpful in helping me to improve the methodology and content of my research. 
    I owe a debt of gratitude to Genoa University's faculty and staff for creating a welcoming learning environment and providing necessary tools for my research. My learning experience has been greatly enhanced by their dedication to excellence. 
    I want to thank my classmates and coworkers for their help and cooperation. They contributed thoughtful ideas, shared their expertise, and took part in insightful discussions. In helping me to develop my ideas and widen my perspective, their contributions have been invaluable. 
    I'm appreciative of my friends' and family's unwavering support, inspiration, and tolerance throughout this difficult academic endeavor. They have been a constant source of inspiration because they believe in me and are present. 
    Finally, I would like to express my sincere gratitude to all the people, groups, and institutions who have kindly helped my research by contributing information, materials, or any other kind of support. This thesis would not have been successful without your assistance. 
    Please know that your contributions have not gone unnoticed and are greatly valued even though it is impossible to specifically thank each individual. 
    I'd like to thank everyone for their encouragement, support, and belief in my abilities. I sincerely appreciate your invaluable contributions to my master's thesis at the University of Genoa, and I do so with the utmost honor and gratitude. 
    percent. 
\end{acknowledgements}
